---
title: "Fuel Prices in Delhi (Assignment 2)"
author: "Rishikesh Pillay"
date: "7/9/2021"
output: html_document
---

# Overview 
Using Plotly I am going show fuel (petrol and diesel) price trend from Jan 2020 to May 2021

This data-set has fuel prices for the city of Delhi. Considering how the fuel prices are rising in India these days, thought this would be a good data-set to have and visualize.

## Content
This data has prices from January 2020 to May 2021. The original data itself is from [mypetrolprice.com](mypetrolprice.com)
And this paticular data-set is from [kaggle](https://www.kaggle.com/rajatrc1705/fuel-prices-delhi-202021)

## Task
I am trying to understand trend or rather understand how fuel (particulary Petrol and Diesel) prices changed in pandemic year 2020 and first half of 2021

# Data loading and getting ready for plotting

```{r read, message=FALSE, warning=FALSE}
library(readr)
library(lubridate)
library(dplyr)
library(reshape2)


df <- read_csv("Data/fuel_prices.csv")
df$date <- dmy(df$date)
fuel <-
        melt(df,
             id = "date",
             measure.vars = c("petrol_price", "diesel_price"))

```

# Trend Using plotly

```{r fig, message=FALSE, warning=FALSE}
library(plotly)
fig <-
        plot_ly(
                data = fuel,
                x = ~ date,
                y =  ~ value,
                color = ~ variable,
                colors = c("#e82088", "#400c99"),
                mode = "line"
        )
fig <-
        fig %>% layout(
                title = "Fuel Prices in Delhi from Jan 2020 to May 2021",
                xaxis = list(title = 'Date'),
                yaxis = list(title = 'Price (India Rupees Rs.)')
        )

fig
```

